The effects of host galaxy properties on merging compact binaries detectable by LIGO

### 2016-07-12 paper/paper.tex
Pushgin

For binary black hole mergers in particular, we show that the present-day binary black hole coalescence rate can vary by factors of several \jillianremark{ UPDATE} in otherwise
similar present-day environments.   Our calculations support and extend prior investigations which demonstrated both
that black hole merger rates depend sensitively on low-metallicitiy environments
\citep[see,e.g.][]{PSellipticals,popsyn-LowMetallicityImpact2b-StarTrackRevised-2013,gwastro-EventPopsynPaper-2016}.   More broadly,
because compact binaries can merge long after they form, their host galaxy can evolve substantially in composition
between birth and merger.
%% and that the delay between compact
%% binary formation and coalesence ccn be
%% the sensitive dependence of binary evolution on
%% metallicity implies that
%% * BBH properties far from apparent.  No surprise: delays can be long , particularly because formation in low Z favored,
%% so system changes significantly from assembly conditions

>>>>

For binary black hole mergers in particular, we show that the present-day binary black hole coalescence rate for our two
Milky-Way like galaxies is nearly identical, independent of their highly distinctive early-time formation histories.   
This result comes as somewhat of a surprise. 
%% can vary by factors of several \jillianremark{ UPDATE} in otherwise
%% similar present-day environments. 
Our calculations adopt the same framework as  prior investigations, which demonstrated 
that black hole merger rates depend sensitively on low-metallicitiy environments
\citep[see,e.g.][]{PSellipticals,popsyn-LowMetallicityImpact2b-StarTrackRevised-2013,gwastro-EventPopsynPaper-2016}.   More broadly,
because compact binaries can merge long after they form, their host galaxy can evolve substantially in composition
between birth and merger.
%% and that the delay between compact
%% binary formation and coalesence ccn be
%% the sensitive dependence of binary evolution on
%% metallicity implies that
%% * BBH properties far from apparent.  No surprise: delays can be long , particularly because formation in low Z favored,
%% so system changes significantly from assembly conditions
Nonetheless, the apparent anticorrelation between the star formation rate and metallicity evolution of our galaxies has
led to similar late-time populations, despite substantial differences early on.
